---
output: 
  pdf_document:
    keep_tex: yes
    fig_caption: yes
    number_sections: yes
geometry: margin=2.54cm
title: "Insert title of project here"
subtitle: "Web address for GitHub repository"
author: "Name"
fontsize: 12pt
mainfont: Times New Roman

---

\newpage
\tableofcontents 
\newpage
\listoftables 
\newpage
\listoffigures 
\newpage

```{r setup, include=FALSE}
# Set your working directory
getwd()


# Load your packages
library(tidyverse)
library(lubridate)
library(trend)
library(forecast)
library(dataRetrieval)
library(rvest)
# Set your ggplot theme
theme_set(theme_classic())
```

```{r datasets: Water Resources Discharge}
#Regular Water Resources
CapeFearRiverDischarge <- readNWISdv(siteNumbers = "02096500",
                                  parameterCd = "00060", # discharge (ft3/s)
                                  startDate = "1990-01-01",
                                  endDate = "2021-12-31")
names(CapeFearRiverDischarge)[4:5] <- c("Discharge", "Approval.Code")
c(min(CapeFearRiverDischarge$Date), max(CapeFearRiverDischarge$Date))
#"1990-01-01" "2021-12-31"
CapeFearRiverDischarge_Monthly <- CapeFearRiverDischarge %>%
  mutate(Month = format(Date,"%Y-%m")) %>%
  group_by(Month) %>%
  summarise(Mean_Discharge_Bymonth = mean(Discharge),
            River = paste("Cape Fear River"))

FlatRiverDischarge <- readNWISdv(siteNumbers = "02085500",
                                  parameterCd = "00060", # discharge (ft3/s)
                                  startDate = "1990-01-01",
                                  endDate = "2021-12-31")
names(FlatRiverDischarge)[4:5] <- c("Discharge", "Approval.Code")
c(min(FlatRiverDischarge$Date), max(FlatRiverDischarge$Date))
#"1990-01-01" "2021-12-31"
FlatRiverDischarge_Monthly <- FlatRiverDischarge %>%
  mutate(Month = format(Date,"%Y-%m")) %>%
  group_by(Month) %>%
  summarise(Mean_Discharge_Bymonth = mean(Discharge),
            River = paste("Flat River"))

LittleRiverDischarge <- readNWISdv(siteNumbers = "0208524975",
                                  parameterCd = "00060", # discharge (ft3/s)
                                  startDate = "1990-01-01",
                                  endDate = "2021-12-31")
names(LittleRiverDischarge)[4:5] <- c("Discharge", "Approval.Code")
c(min(LittleRiverDischarge$Date), max(LittleRiverDischarge$Date))
#"1995-10-24" "2021-12-31"
LittleRiverDischarge_Monthly <- LittleRiverDischarge %>%
  mutate(Month = format(Date,"%Y-%m")) %>%
  group_by(Month) %>%
  summarise(Mean_Discharge_Bymonth = mean(Discharge),
            River = paste("Little River"))

#Emergency Water Resources
EnoRiverDischarge <- readNWISdv(siteNumbers = "02085070",
                                  parameterCd = "00060", # discharge (ft3/s)
                                  startDate = "1990-01-01",
                                  endDate = "2021-12-31")
names(EnoRiverDischarge)[4:5] <- c("Discharge", "Approval.Code")
c(min(EnoRiverDischarge$Date), max(EnoRiverDischarge$Date))
#"1990-01-01" "2021-12-31"
EnoRiverDischarge_Monthly <- EnoRiverDischarge %>%
  mutate(Month = format(Date,"%Y-%m")) %>%
  group_by(Month) %>%
  summarise(Mean_Discharge_Bymonth = mean(Discharge),
            River = paste("Eno River"))

#Surrounding Water Resources (Unused)
EllerbeCreekDischarge <- readNWISdv(siteNumbers = "0208675010",
                                  parameterCd = "00060", # discharge (ft3/s)
                                  startDate = "1990-01-01",
                                  endDate = "2021-12-31")
names(EllerbeCreekDischarge)[4:5] <- c("Discharge", "Approval.Code")
c(min(EllerbeCreekDischarge$Date), max(EllerbeCreekDischarge$Date))
#"2008-08-01" "2021-12-31"
EllerbeCreekDischarge_Monthly <- EllerbeCreekDischarge %>%
  mutate(Month = format(Date,"%Y-%m")) %>%
  group_by(Month) %>%
  summarise(Mean_Discharge_Bymonth = mean(Discharge),
            River = paste("Ellerbe Creek"))

SandyCreekDischarge <- readNWISdv(siteNumbers = "0209722970",
                                  parameterCd = "00060", # discharge (ft3/s)
                                  startDate = "1990-01-01",
                                  endDate = "2021-12-31")
names(SandyCreekDischarge)[4:5] <- c("Discharge", "Approval.Code")
c(min(SandyCreekDischarge$Date), max(SandyCreekDischarge$Date))
#"2008-08-01" "2021-12-31"
SandyCreekDischarge_Monthly <- SandyCreekDischarge %>%
  mutate(Month = format(Date,"%Y-%m")) %>%
  group_by(Month) %>%
  summarise(Mean_Discharge_Bymonth = mean(Discharge),
            River = paste("Sandy Creek"))

ThirdForkCreekDischarge <- readNWISdv(siteNumbers = "0209725960",
                                  parameterCd = "00060", # discharge (ft3/s)
                                  startDate = "1990-01-01",
                                  endDate = "2021-12-31")
names(ThirdForkCreekDischarge)[4:5] <- c("Discharge", "Approval.Code")
c(min(ThirdForkCreekDischarge$Date), max(ThirdForkCreekDischarge$Date))
#"2017-06-16" "2021-12-31"
ThirdForkCreekDischarge_Monthly <- ThirdForkCreekDischarge %>%
  mutate(Month = format(Date,"%Y-%m")) %>%
  group_by(Month) %>%
  summarise(Mean_Discharge_Bymonth = mean(Discharge),
            River = paste("Third Fork Creek"))

```

```{r Groundwater}
GroundParams <- whatNWISdata(siteNumbers = "355944079013401")
DurhamGroundwater <- readNWISdv(siteNumbers = "355852078572045",
                                 parameterCd = "62610", # /72019/Groundwater level above NGVD 1929 (feet)
                                 startDate = "2009-01-01",
                                 endDate = "2021-12-31")
names(DurhamGroundwater)[4:5] <- c("Groundwater", "Approval.Code")
c(min(DurhamGroundwater$Date), max(DurhamGroundwater$Date))
#
```

```{r Total Withdrawl}
#the PSWID of Durham
durham_pswid = '03-32-010'
#years with records
the_years = c(2018:2021)

#Scrap Function
scrape.totalwithdrawal <- function(the_pswid, the_year){
  the_website <- read_html(paste0('https://www.ncwater.org/WUDC/app/LWSP/report.php?pwsid=', 
                                  the_pswid, '&year=', the_year))
  
  water_system_name_tag <- 'div+ table tr:nth-child(1) td:nth-child(2)'
  ownership_tag <- 'div+ table tr:nth-child(2) td:nth-child(4)'
  avg_daily_use_tag <- '.fancy-table:nth-child(31) th+ td'
  
  water_system_name <- the_website %>% html_nodes(water_system_name_tag) %>% html_text()
  ownership <- the_website %>%   html_nodes(ownership_tag) %>%  html_text()
  avg_daily_use <- the_website %>% html_nodes(avg_daily_use_tag) %>% html_text()
  
  df_withdrawals <- data.frame("Year" = rep(the_year,12),
                               "Month" = rep(1:12),
                               "Avg_Daily_Use_mgd" = as.numeric(avg_daily_use)) %>% 
    mutate(Water_System_name = !!water_system_name,
         Ownership = !!ownership,
         Date = my(paste(Month,"-",Year)))
  
  print(paste('The Pswid =', the_pswid, ', The Year =', the_year))
  return(df_withdrawals)
}

total_withdrawal <- map(the_years, scrape.totalwithdrawal, the_pswid = durham_pswid)
total_withdrawal <- bind_rows(total_withdrawal)
```

```{r Withdrawal Distribution}
#the PSWID of Durham
durham_pswid = '03-32-010'
#years with records
the_years = c(2018:2021)

scrape.withdrawal.distribution <- function(the_pswid, the_year){
  the_website <- read_html(paste0('https://www.ncwater.org/WUDC/app/LWSP/report.php?pwsid=', 
                                  the_pswid, '&year=', the_year))
  
  water_system_name_tag <- 'div+ table tr:nth-child(1) td:nth-child(2)'
  ownership_tag <- 'div+ table tr:nth-child(2) td:nth-child(4)'
  stream_name_tag <- '.fancy-table:nth-child(35) .left:nth-child(1)'
  avg_daily_use_tag <- '.fancy-table:nth-child(35) .left~ .left+ td'
  the_numberofdaysused_tag <- '.fancy-table:nth-child(35) td:nth-child(4)'
  
  water_system_name <- the_website %>% html_nodes(water_system_name_tag) %>% html_text()
  ownership <- the_website %>%   html_nodes(ownership_tag) %>%  html_text()
  stream_name <- the_website %>% html_nodes(stream_name_tag) %>% html_text()
  avg_daily_use <- the_website %>% html_nodes(avg_daily_use_tag) %>% html_text()
  the_numberofdaysused <- the_website %>% html_nodes(the_numberofdaysused_tag) %>% html_text()
  
  df_withdrawals <- data.frame("Year" = rep(the_year,5),
                               "Stream_Name" = stream_name,
                               "Avg_Daily_Use_mgd" = as.numeric(avg_daily_use),
                               "Number_of_Days_Used" = as.numeric(the_numberofdaysused)) %>% 
    mutate(Water_System_name = !!water_system_name,
         Ownership = !!ownership)
  
  print(paste('The Pswid =', the_pswid, ', The Year =', the_year))
  return(df_withdrawals)
}

withdrawal_distribution <- map(the_years, scrape.withdrawal.distribution, the_pswid = durham_pswid)
withdrawal_distribution <- bind_rows(withdrawal_distribution)
```

```{r Industry Withdrawl}
#Water-use industries' sites 
#https://www.ncwater.org/WUDC/app/WWATR/report
Brentwood <- "0218-0068"
CanterburyEstates <- "0218-0086"
CardensCreek <- "0218-0088"
FoxRun <- "0218-0199"
Greymoss <- "0218-0229"
Hardscrabble <- "0218-0238"
LakeRidge <- "0218-0313"
Masonwoods <- "0218-0349"
RedMountain <- "0218-0460"
TrappersCreek <- "0218-0608"
Tyndrum <- "0218-0619"
Wexford <- "0218-0646"
WillowHill <- "0218-0658"
HeatherGlen <- "0378-0038"
ColvardFarms <- "0427-0001"
CroasdaileCountryClub <- "0419-0001"
RougemontQuarry <- "0340-0003"
Durham.sites <- c(Brentwood, CanterburyEstates, CardensCreek, FoxRun, Greymoss, Hardscrabble, LakeRidge, Masonwoods, RedMountain, TrappersCreek, Tyndrum, Wexford, WillowHill, HeatherGlen, ColvardFarms, CroasdaileCountryClub, RougemontQuarry)

#years with records
the_years = c(2007:2021)

#Scraping Function
scrape.industrywithdrawals <- function(the_year, the_facility){
  #Retrieve the website contents 
  the_website <- read_html(paste0('https://www.ncwater.org/WUDC/app/WWATR/report/view/', 
                                  the_facility, '/', the_year))
  
  #Set the element address variables (determined in the previous step)
  the_registrant_tag <- '.table tr:nth-child(1) td:nth-child(2)'
  the_facility_name_tag <- 'tr:nth-child(2) th+ .left:nth-child(2)'
  the_facility_id_tag <- 'tr:nth-child(2) .left~ .left+ td.left'
  the_data_tag <- '.table:nth-child(7) td:nth-child(7) , .table:nth-child(7) td:nth-child(3)'
  the_numberofdaysused_tag <- '.table:nth-child(7) th+ td'
  
  #Scrape the data items
  the_registrant <- the_website %>% html_nodes(the_registrant_tag) %>% html_text()
  the_facility_name <- the_website %>%   html_nodes(the_facility_name_tag) %>%  html_text()
  the_facility_type <- the_website %>% html_nodes(the_facility_id_tag) %>% html_text()
  avg_withdrawals <- the_website %>% html_nodes(the_data_tag) %>% html_text()
  the_numberofdaysused <- the_website %>% html_nodes(the_numberofdaysused_tag) %>% html_text()
  
  #Convert to a dataframe
  df_withdrawals <- data.frame("Year" = rep(the_year,12),
                               "Month" = rep(1:12),
                               "Avg_Withdrawals_mgd" = as.numeric(avg_withdrawals),
                               "Number_of_Days_Used" = as.numeric(the_numberofdaysused)) %>% 
    mutate(Registrant = !!the_registrant,
           Facility_name = !!the_facility_name,
           Facility_type = !!the_facility_type,
           Date = my(paste(Month,"-",Year)))
  
  #Pause for a moment - scraping etiquette
  #Sys.sleep(1) #uncomment this if you are doing bulk scraping!
  
  #Return the dataframe
  return(df_withdrawals)
}

industry_withdrawal <- cross2(the_years, Durham.sites) %>% 
  map(lift(scrape.industrywithdrawals)) %>% 
  bind_rows()
```

```{r Precipitation}
#Precipitation
PreciParams <- whatNWISdata(siteNumbers = "355852078572045")
DurhamPrecipitaion <- readNWISdv(siteNumbers = "355852078572045",
                                 parameterCd = "00065", # precipitation (inches)
                                 startDate = "2009-01-01",
                                 endDate = "2021-12-31")
names(DurhamPrecipitaion)[4:5] <- c("Precipitaion", "Approval.Code")
c(min(DurhamPrecipitaion$Date), max(DurhamPrecipitaion$Date))
#
```

```{r Total Wastewater}
#the PSWID of Durham
durham_pswid = '03-32-010'
#years with records
the_years = c(2018:2021)

scrape.totalwastewater <- function(the_pswid, the_year){
  the_website <- read_html(paste0('https://www.ncwater.org/WUDC/app/LWSP/report.php?pwsid=', 
                                  the_pswid, '&year=', the_year))
  
  water_system_name_tag <- 'div+ table tr:nth-child(1) td:nth-child(2)'
  ownership_tag <- 'div+ table tr:nth-child(2) td:nth-child(4)'
  avg_daily_discharge_tag <- '.fancy-table:nth-child(50) td'
  
  water_system_name <- the_website %>% html_nodes(water_system_name_tag) %>% html_text()
  ownership <- the_website %>%   html_nodes(ownership_tag) %>%  html_text()
  avg_daily_discharge <- the_website %>% html_nodes(avg_daily_discharge_tag) %>% html_text()
  
  df_wastewaters <- data.frame("Year" = rep(the_year,12),
                               "Month" = rep(1:12),
                               "Avg_Daily_Use_mgd" = as.numeric(avg_daily_discharge)) %>% 
    mutate(Water_System_name = !!water_system_name,
         Ownership = !!ownership,
         Date = my(paste(Month,"-",Year)))
  
  print(paste('The Pswid =', the_pswid, ', The Year =', the_year))
  return(df_wastewaters)
}

total_wastewater <- map(the_years, scrape.totalwastewater, the_pswid = durham_pswid)
total_wastewater <- bind_rows(total_wastewater)
```

```{r Wastewater Distribution}
#the PSWID of Durham
durham_pswid = '03-32-010'
#years with records
the_years = c(2018:2021)

scrape.wastewater.distribution <- function(the_pswid, the_year){
  the_website <- read_html(paste0('https://www.ncwater.org/WUDC/app/LWSP/report.php?pwsid=', 
                                  the_pswid, '&year=', the_year))
  
  water_system_name_tag <- 'div+ table tr:nth-child(1) td:nth-child(2)'
  ownership_tag <- 'div+ table tr:nth-child(2) td:nth-child(4)'
  stram_name_tag <- '.fancy-table:nth-child(55) .left:nth-child(6)'
  basin_name_tag <- '.left:nth-child(7)'
  avg_daily_discharge_tag <- '.fancy-table:nth-child(55) td:nth-child(4)'

  water_system_name <- the_website %>% html_nodes(water_system_name_tag) %>% html_text()
  ownership <- the_website %>%   html_nodes(ownership_tag) %>%  html_text()
  stream_name <- the_website %>% html_nodes(stram_name_tag) %>% html_text()
  basin_name <- the_website %>% html_nodes(basin_name_tag) %>% html_text()
  avg_daily_discharge <- the_website %>% html_nodes(avg_daily_discharge_tag) %>% html_text()

  df_wastewater <- data.frame("Year" = rep(the_year,2),
                               "Recieving_Stream" = stream_name,
                              "Recieving_Basin" = basin_name,
                               "Avg_Daily_Discharge_mgd" = as.numeric(avg_daily_discharge)) %>% 
    mutate(Water_System_name = !!water_system_name,
         Ownership = !!ownership)
  
  print(paste('The Pswid =', the_pswid, ', The Year =', the_year))
  return(df_wastewater)
}

wastewater_distribution <- map(the_years, scrape.wastewater.distribution, the_pswid = durham_pswid)
wastewater_distribution <- bind_rows(wastewater_distribution)
```

```{r time-series analysis on Regular Water Resources}
CapeFearRiver_timeseries <- ts(CapeFearRiverDischarge_Monthly$Mean_Discharge_Bymonth, frequency = 12,
                           start = c(1990, 1, 1), end = c(2021, 12, 1))
CapeFearRiver_Decomposed <- stl(CapeFearRiver_timeseries, s.window = "periodic")
plot(CapeFearRiver_Decomposed)

CapeFearRiver_trend <- smk.test(CapeFearRiver_timeseries)
CapeFearRiver_trend
summary(CapeFearRiver_trend)
#p-value is 0.3233, so there is no trend present in Cape Fear River.

FlatRiver_timeseries <- ts(FlatRiverDischarge_Monthly$Mean_Discharge_Bymonth, frequency = 12,
                           start = c(1990, 1, 1), end = c(2021, 12, 1))
FlatRiver_Decomposed <- stl(FlatRiver_timeseries, s.window = "periodic")
plot(FlatRiver_Decomposed)

FlatRiver_trend <- smk.test(FlatRiver_timeseries)
FlatRiver_trend
summary(FlatRiver_trend)
#p-value is 0.3968, so there is no trend present in Flat River.

LittleRiver_timeseries <- ts(LittleRiverDischarge_Monthly$Mean_Discharge_Bymonth, frequency = 12,
                           start = c(1990, 1, 1), end = c(2021, 12, 1))
LittleRiver_Decomposed <- stl(LittleRiver_timeseries, s.window = "periodic")
plot(LittleRiver_Decomposed)

LittleRiver_trend <- smk.test(LittleRiver_timeseries)
LittleRiver_trend
summary(LittleRiver_trend)
#p-value is 0.4073, so there is no trend present in Little River.
```

```{r time-series analysis on withdrawals}
total_withdrawal_timeseries <- ts(total_withdrawal$Avg_Daily_Use_mgd, frequency = 12,
                           start = c(2018, 1, 1), end = c(2021, 12, 1))
total_withdrawal_Decomposed <- stl(total_withdrawal_timeseries, s.window = "periodic")
plot(total_withdrawal_Decomposed)

total_withdrawal_trend <- smk.test(total_withdrawal_timeseries)
total_withdrawal_trend
summary(total_withdrawal_trend)
#p-value is 0.3775, so there is no trend present in Cape Fear River.
```

# Rationale and Research Questions



\newpage

# Dataset Information



\newpage

# Exploratory Analysis 



\newpage

# Analysis



## Question 1: <insert specific question here and add additional subsections for additional questions below, if needed> Is there a relationship between surface water flow and groundwater levels in Durham region?

## Question 2: How much is surface water affected by municipal withdrawal and precipitation recharge?




\newpage

# Summary and Conclusions


\newpage

# References
<add references here if relevant, otherwise delete this section> 
